Synthesizing Quotient Lenses

### 2017-10-17 papers/QuotientLensSynth/main.tex
add commands

@@

To test if our tool eases the development process, we compare the following
number of AST nodes.
%
\begin{itemize}
\item[QRESize{}] QRESize{} is the number of AST nodes in the QRE
  specifications involved in QRE lens synthesis task.
\item[CanonizerAndSpecSize{}] CanonizerAndSpecSize{} is the number of
  AST nodes in $W(q)$ summed with the number of AST nodes in $\canonizer(q)$,
  for each QRE used in QRE lens synthesis task.
\item[LensAndSpecSize{}] LensAndSpecSize{} is the number of AST nodes
  in $W(q)$ summed with the number of AST nodes in the synthesized QRE lens.
\end{itemize}

The value of QRESize{} represents the difficulty in writing our benchmarks.

The value of CanonizerAndSpecSize{} represents the difficulty in writing our
benchmarks without QREs.  This is only an approximation, as both $W(q)$ and
$\canonizer(q)$ are automatically generated from the QRE.  In our
experience, these automatically generated regular expressions and canonizers are
the ones we would naturally write.

The value of LensAndSpecSize{} represents the difficulty in writing our benchmarks
with neither QREs nor synthesis.  This is also an approximation, as $W(q)$ and
$\canonizer(q)$ and the bijective lens are all automatically generated.
We have found that the generated bijective lens is fairly similar in size to the
one we would manually write, though it is typically less modular.

Figure~\ref{?} shows the number of benchmarks written with at most a given
number of AST nodes.  We found that QRESize{} was consistently smaller than
CanonizerAndSpecSize{} and LensAndSpecSize{}, demonstrating that introducing
QREs saves programmers programming effort compared to both Optician and basic
Boomerang.

>>>>

\newcommand{\QRESize}{QS}
\newcommand{\CanonizerAndSpecSize}{CS}
\newcommand{\LensAndSpecSize}{LS}

@@

To test if our tool eases the development process, we compare the following
number of AST nodes.
%
\begin{itemize}
\item[\QRESize{}] \QRESize{} is the number of AST nodes in the QRE
  specifications involved in QRE lens synthesis task.
\item[\CanonizerAndSpecSize{}] \CanonizerAndSpecSize{} is the number of
  AST nodes in $W(q)$ summed with the number of AST nodes in $\canonizer(q)$,
  for each QRE used in QRE lens synthesis task.
\item[\LensAndSpecSize{}] \LensAndSpecSize{} is the number of AST nodes
  in $W(q)$ summed with the number of AST nodes in the synthesized QRE lens.
\end{itemize}

The value of \QRESize{} represents the difficulty in writing our benchmarks.

The value of \CanonizerAndSpecSize{} represents the difficulty in writing our
benchmarks without QREs.  This is only an approximation, as both $W(q)$ and
$\canonizer(q)$ are automatically generated from the QRE.  In our
experience, these automatically generated regular expressions and canonizers are
the ones we would naturally write.

The value of \LensAndSpecSize{} represents the difficulty in writing our benchmarks
with neither QREs nor synthesis.  This is also an approximation, as $W(q)$ and
$\canonizer(q)$ and the bijective lens are all automatically generated.
We have found that the generated bijective lens is fairly similar in size to the
one we would manually write, though it is typically less modular.

Figure~\ref{?} shows the number of benchmarks written with at most a given
number of AST nodes.  We found that \QRESize{} was consistently smaller than
\CanonizerAndSpecSize{} and \LensAndSpecSize{}, demonstrating that introducing
QREs saves programmers programming effort compared to both Optician and basic
Boomerang.
